### 2013-04-29 inst/examples/BUGS/allen.Rmd
uniform prior on variances

```{r libraries, cache=FALSE}
library(pdgControl) # custom SDP functions
library(nonparametricbayes) # custom 
library(reshape2) # data manipulation
library(data.table) # data manipulation
library(plyr) # data manipulation
library(ggplot2) # plotting 
library(tgp) # Gaussian Processes
library(MCMCpack) # Markov Chain Monte Carlo tools 
library(R2jags) # Markov Chain Monte Carlo tools 
library(emdbook) # Markov Chain Monte Carlo tools 
library(coda) # Markov Chain Monte Carlo tools 
```

@@

Uses the model derived in `r citet("")`, of a Ricker-like growth curve with an allee effect, defined in the pdgControl package,

@@

```{r}
cat(readLines(con="bugmodel-GammaPrior.txt"), sep="\n")
```

@@

```{r}
jags.params=c("K","logr0","logtheta","iR","iQ") # Don't need to save "x"
jags.inits <- function(){
  list("K"=init_p["K"],"logr0"=log(init_p["r0"]),"logtheta"=log(init_p["theta"]),"iQ"=1/0.05,"iR"=1/0.1,"x"=y,.RNG.name="base::Wichmann-Hill", .RNG.seed=123)
}
set.seed(12345)
time<-system.time(       
  jagsfit <- jags(data=jags.data, inits=jags.inits, jags.params, n.chains=n.chains, 
                  n.iter=n.iter, n.thin=n.thin, n.burnin=n.burnin,model.file="bugmodel-GammaPrior.txt")
)         
time <- unname(time["elapsed"]);
```

@@

```{r}
mcmc <- as.mcmc(jagsfit)
mcmcall <- mcmc[,-2]
who <- colnames(mcmcall)
who 
mcmcall <- cbind(mcmcall[,1],mcmcall[,2],mcmcall[,3],mcmcall[,4],mcmcall[,5])
colnames(mcmcall) <- who
```

#### Phase-space diagram of the expected dynamics

```{r}
  gp_plot(gp, f, p, est$f, est$p, alt$f, alt$p, x_grid, obs, seed_i)
```

>>>>

```{r libraries, cache=FALSE, message=FALSE, warning=FALSE}
library(pdgControl) # custom SDP functions
library(nonparametricbayes) # custom 
library(reshape2) # data manipulation
library(data.table) # data manipulation
library(plyr) # data manipulation
library(ggplot2) # plotting 
library(tgp) # Gaussian Processes
library(MCMCpack) # Markov Chain Monte Carlo tools 
library(R2jags) # Markov Chain Monte Carlo tools 
library(emdbook) # Markov Chain Monte Carlo tools 
library(coda) # Markov Chain Monte Carlo tools 
```

@@

Uses the model derived in `r citet("10.1080/10236190412331335373")`, of a Ricker-like growth curve with an allee effect, defined in the pdgControl package,

@@

```{r}
cat(readLines(con="bugmodel-UPrior.txt"), sep="\n")
```

@@

```{r}
jags.params=c("K","logr0","logtheta","iR","iQ") # Don't need to save "x"
#jags.inits <- function(){ list("K"=init_p["K"],"logr0"=log(init_p["r0"]),"logtheta"=log(init_p["theta"]),"iQ"=1/0.05,"iR"=1/0.1,"x"=y,.RNG.name="base::Wichmann-Hill", .RNG.seed=123) }

jags.params=c("K","logr0","logtheta","stdQ", "stdR")
jags.inits <- function(){
  list("K"=init_p["K"],"logr0"=log(init_p["r0"]),"logtheta"=log(init_p["theta"]), "stdQ"=sqrt(0.05),"stdR"=sqrt(0.1),"x"=y,.RNG.name="base::Wichmann-Hill", .RNG.seed=123)
}

set.seed(12345)

time<-system.time(       
  jagsfit <- jags(data=jags.data, inits=jags.inits, jags.params, n.chains=n.chains, 
                  n.iter=n.iter, n.thin=n.thin, n.burnin=n.burnin,model.file="bugmodel-UPrior.txt")
)         
time <- unname(time["elapsed"]);
```

@@

```{r}
mcmc <- as.mcmc(jagsfit)
mcmcall <- mcmc[,-2]
who <- colnames(mcmcall)
who 
mcmcall <- cbind(mcmcall[,1],mcmcall[,2],mcmcall[,3],mcmcall[,4],mcmcall[,5])
colnames(mcmcall) <- who

bayes_coef <- apply(mcmcall,2,mean)
bayes_pars <- c(bayes_coef[4], bayes_coef[1], bayes_coef[5])

### Phase-space diagram of the expected dynamics

```{r}
# Summarize the GP model
tgp_dat <- 
    data.frame(  x = gp$XX[[1]], 
                 y = gp$ZZ.km, 
                 ymin = gp$ZZ.km - 1.96 * sqrt(gp$ZZ.ks2), 
                 ymax = gp$ZZ.km + 1.96 * sqrt(gp$ZZ.ks2),
                 ymin2 = gp$ZZ.mean - 1.96 * sqrt(gp$ZZ.vark), 
                 ymax2 = gp$ZZ.mean + 1.96 * sqrt(gp$ZZ.vark))

  true_means <- sapply(x_grid, f, 0, p)
  alt_means <- sapply(x_grid, alt$f, 0, alt$p)
  est_means <- sapply(x_grid, est$f, 0, est$p)
  par_bayes_means <- sapply(x_grid, est$f, 0, bayes_pars)

models <- data.frame(x=x_grid, GP=tgp_dat$y, True=true_means, 
                     MLE=est_means, Ricker.MLE=alt_means, 
                     Parametric.Bayes = par_bayes_means)

  models <- melt(models, id="x")
  names(models) <- c("x", "method", "value")

  plot_gp <- ggplot(tgp_dat) + geom_ribbon(aes(x,y,ymin=ymin,ymax=ymax), fill="gray80") +
    geom_ribbon(aes(x,y,ymin=ymin2,ymax=ymax2), fill="gray60") +
    geom_line(data=models, aes(x, value, col=method), lwd=2, alpha=0.8) + 
    geom_point(data=obs, aes(x,y), alpha=0.8) + 
    xlab(expression(X[t])) + ylab(expression(X[t+1])) +
    scale_colour_manual(values=cbPalette) 
  print(plot_gp)
```
